A generalized definition of multidimensional item response theory parameters

### 2024-09-06 output/Main_text.Rmd
Adds libraries to prevent {renv} inconsistencies

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)

>>>>

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)
library(rsvg)    # Used by {knitr} and {ggplot2} to render the figure to SVG;
library(svglite) #   added to prevent {renv} from reporting inconsistent state.
